A highly-available move operation for replicated trees

### 2021-02-26 paper/move-op.tex
Add Patreon supporters

The authors wish to acknowledge the support of The Boeing Company and the EPSRC ``REMS: Rigorous Engineering for Mainstream Systems'' programme grant (EP/K008528).
Martin Kleppmann is supported by a Leverhulme Trust Early Career Fellowship, the Isaac Newton Trust, and Nokia Bell Labs.
Our evaluation was conducted using AWS credits from the AWS Educate program.
Thank you to Marc Shapiro for feedback on a draft of this paper.

>>>>

The authors wish to acknowledge the support of The Boeing Company and the EPSRC ``REMS: Rigorous Engineering for Mainstream Systems'' programme grant (EP/K008528).
Martin Kleppmann is supported by a Leverhulme Trust Early Career Fellowship, the Isaac Newton Trust, Nokia Bell Labs, and crowdfunding supporters including Molham Aref, Henry Caushi, Chet Corcos, Gabriel Herrero-Beaumont, Bogdan Kanivets, David Pollak, SoftwareMill, Talent Formation Network, and Adam Wiggins.
Our evaluation was conducted using AWS credits from the AWS Educate program.
Thank you to Marc Shapiro for feedback on a draft of this paper.
